\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{xcolor}
\definecolor{customblue}{HTML}{4174c5}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1.8pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}

\renewcommand\labelitemi{\textbullet}
\renewcommand\labelitemii{\textbullet}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label=\textbullet, leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{{\LARGE Mohit Adhikari}} \\
    \vspace{+5pt}
    D-46, West Vinod Nagar, Delhi, India \\
    \vspace{+5pt}
    \textcolor{customblue}{\href{mailto:mohitadhikari2002@gmail.com}{mohitadhikari2002@gmail.com}} $|$ 
    \textcolor{customblue}{\href{tel:+919310194960}{+91 9310194960}} $|$ 
    \textcolor{customblue}{\href{https://www.linkedin.com/in/mohit-adhikari-69b026238/}{LinkedIn}} $|$ 
    \textcolor{customblue}{\href{https://github.com/mohitadhikari123}{GitHub}}
\end{center}

\vspace{-20pt}

%-----------SUMMARY-----------
\section{Summary}
\resumeSubHeadingListStart
\item
\resumeItemListStart
\resumeItem{Enthusiastic and detail-oriented Junior Front End Engineer with a foundational understanding of ReactJS and Node.js, eager to contribute to a dynamic engineering team. Proficient in modern JavaScript (ES6+) and TypeScript, with a solid grasp of HTML5, CSS3, and responsive web design principles. Collaborative and quick learner with strong problem-solving skills, adept at writing clean, testable code and participating in code reviews. Eager to learn new technologies and contribute to project goals, while providing support for existing applications and creating technical documentation. Familiar with foundational AI concepts and code generation tools.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\vspace{5pt}
\resumeSubHeadingListStart

\resumeSubheading
{Digital Guruji}{April 2025 -- Present}
{Full Stack Developer Intern}{Delhi}
\resumeItemListStart
\resumeItem{Led the development and launch of Airbrush.ai, an AI-powered image generation platform using ReactJS and Node.js, enabling users to generate photorealistic images with a single click, demonstrating strong problem-solving skills and attention to detail.}
\resumeItem{Ensured high availability and performance by achieving 99\% uptime and accelerating image generation speed by 40\% through strategic performance optimizations, while incorporating user feedback to refine the platform and improve user experience. Focused on writing clean and efficient code, and actively participating in code reviews.}
\resumeItemListEnd

\resumeSubheading
{Rialtes Technologies and Solution LLP}{Jan 2024 -- April 2024}
{Software Trainee}{Dehradun}
\resumeItemListStart
\resumeItem{Spearheaded the design and development of the company's corporate website using JavaScript, React.js, Node.js, and MongoDB, emphasizing a user-friendly interface and showcasing Rialtes' Salesforce and SAP B2B solutions to prospective clients. Applied web development best practices throughout the project.}
\resumeItem{Enhanced brand visibility by optimizing website performance and SEO, resulting in a 30\% increase in online inquiries and improved brand visibility among target B2B audiences, demonstrating business acumen and strategic thinking. Utilized Git for version control and collaborated with a team to meet project goals.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\href{https://furniro-neon-rho.vercel.app/}{\textbf{\textcolor{customblue}{Furniro - Ecommerce Website for Furniture}}} $|$ \emph{React.js, Node.js, MongoDB, Redux Toolkit, Stripe}}
{}
\resumeItemListStart
\resumeItem{\textbf{Application:} Developed a full-stack ecommerce platform with product listings, cart, checkout, and secure payments, demonstrating proficiency in ReactJS and Node.js.}
\resumeItem{\textbf{User Features:} Added categories, search, filtering, and favorites for personalized shopping, enhancing the user experience with responsive web design principles.}
\resumeItem{\textbf{Impact:} Delivered responsive UI and faster load times, boosting user engagement and showcasing an understanding of performance optimization concepts.}
\resumeItem{\textbf{Impact:} Increased conversion rate by 25\% through streamlined checkout flow and optimized UX, demonstrating an understanding of business requirements and user-centric design.}
\resumeItem{\textbf{Performance:} Integrated Stripe and optimized queries, reducing transaction time by 35\%, demonstrating API interaction skills and problem-solving abilities.}
\resumeItemListEnd



\vspace{-15pt}

\resumeProjectHeading
{\href{https://smart-recruit-green.vercel.app/}{\textbf{\textcolor{customblue}{Smart Recruit - AI-Powered Candidate Evaluation Platform}}} $|$ \emph{Next.js, Gemini API, CSS, MongoDB}}
{}
\resumeItemListStart
\resumeItem{\textbf{Application:} Built an AI tool for HRs to evaluate candidates by comparing resumes with job descriptions, leveraging foundational AI concepts and Next.js for efficient development.}
\resumeItem{\textbf{Key Features:} Added compatibility scoring, feedback (skills, experience, gaps), and ranking for better hiring decisions, showcasing analytical skills and a focus on problem-solving.}
\resumeItem{\textbf{Responsive Design:} Delivered consistent user experience across devices, demonstrating understanding of HTML5, CSS3, and responsive web design principles.}
\resumeItem{\textbf{Impact:} Achieved 90\% accuracy in job-candidate matching using AI-driven resume parsing, highlighting a practical application of AI code generation techniques.}
\resumeItem{\textbf{Impact:} Reduced candidate screening time by 40\%, improving recruiter efficiency and decision-making speed, reflecting an understanding of software development practices and their impact on business processes.}
\resumeItemListEnd



\resumeSubHeadingListEnd
\vspace{-10pt}

%-----------SKILLS-----------
\section{Skills Summary}
\vspace{5pt}
\begin{itemize}[leftmargin=0.15in, label={}]
\item
\small{\textbf{Technical Skills:} JavaScript (ES6+), TypeScript, HTML5, CSS3, RESTful APIs, Git, Unit Testing.} \\
\item
\small{\textbf{Frameworks and Libraries:} React.js, Next.js, Node.js, Express.js, Redux (Exposure).} \\
\item
\small{\textbf{Databases:} MongoDB (NoSQL with Mongoose).} \\
\item
\small{\textbf{Tools and Platforms:} Git, GitHub, VSCode, Vercel, Render} \\
\item
\small{\textbf{Development Expertise:} Agile methodologies, Responsive Design, Cross-Device Interfaces, API Integration, Data Fetching, Error Handling, Performance Optimization, Code Review Participation, Bug Fixing.}
\end{itemize}

%-----------EDUCATION及ひび-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Bipin Tripathi Kumaun Institute of Technology Dwarahat, Almora}{Uttarakhand, India}
{Bachelor of Technology; CGPA: 7.1}{August 2020 -- June 2024}
\resumeSubHeadingListEnd

\end{document}
