\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{xcolor}
\definecolor{customblue}{HTML}{4174c5}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1.8pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}

\renewcommand\labelitemi{\textbullet}
\renewcommand\labelitemii{\textbullet}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label=\textbullet, leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{{\LARGE Mohit Adhikari}} \\
    \vspace{+5pt}
    D-46, West Vinod Nagar, Delhi, India \\
    \vspace{+5pt}
    \textcolor{customblue}{\href{mailto:mohitadhikari2002@gmail.com}{mohitadhikari2002@gmail.com}} $|$ 
    \textcolor{customblue}{\href{tel:+919310194960}{+91 9310194960}} $|$ 
    \textcolor{customblue}{\href{https://www.linkedin.com/in/mohit-adhikari-69b026238/}{LinkedIn}} $|$ 
    \textcolor{customblue}{\href{https://github.com/mohitadhikari123}{GitHub}}
\end{center}

\vspace{-20pt}

%-----------SUMMARY-----------
\section{Summary}
\resumeSubHeadingListStart
\item
\resumeItemListStart
\resumeItem{A highly motivated and collaborative Full Stack Developer with a passion for software development and a strong understanding of frontend and backend technologies. Proficient in designing user interfaces and developing scalable web applications using JavaScript, TypeScript, React, Next.js, and Node.js. Expertise in API integrations, responsive design, and performance optimization. Possesses strong problem-solving skills, good communication and teamwork skills, and a proven ability to deliver high-quality code and user-centric solutions under deadlines.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\vspace{5pt}
\resumeSubHeadingListStart

\resumeSubheading
{Digital Guruji}{April 2025 -- Present}
{Full Stack Developer Intern}{Delhi}
\resumeItemListStart
\resumeItem{Led the development and launch of Airbrush.ai, an AI-powered image generation platform, from inception, enabling users to generate photorealistic images with a single click, demonstrating strong problem-solving skills, attention to detail, and software development best practices.}
\resumeItem{Ensured high availability and performance by achieving 99\% uptime and accelerating image generation speed by 40\% through strategic performance optimizations, while incorporating user feedback to refine the platform and improve user experience. Showcased analytical skills and a collaborative approach in enhancing the platform.}
\resumeItemListEnd

\resumeSubheading
{Rialtes Technologies and Solution LLP}{Jan 2024 -- April 2024}
{Software Trainee}{Dehradun}
\resumeItemListStart
\resumeItem{Spearheaded the design and development of the company's corporate website using JavaScript, React.js, Node.js, and MongoDB, emphasizing a user-friendly interface and showcasing Rialtes' Salesforce and SAP B2B solutions to prospective clients. Demonstrated proficiency in frontend and backend technologies.}
\resumeItem{Enhanced brand visibility by optimizing website performance and SEO, resulting in a 30\% increase in online inquiries and improved brand visibility among target B2B audiences, demonstrating business acumen, strategic thinking, and effective communication skills.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\href{https://furniro-neon-rho.vercel.app/}{\textbf{\textcolor{customblue}{Furniro - Ecommerce Website for Furniture}}} $|$ \emph{React.js, Node.js, MongoDB, Redux Toolkit, Stripe}}
{}
\resumeItemListStart
\resumeItem{\textbf{Application:} Developed a full-stack ecommerce platform with product listings, cart, checkout, and secure payments, applying software development practices to create a responsive application.}
\resumeItem{\textbf{User Features:} Added categories, search, filtering, and favorites for personalized shopping, focusing on UI/UX to improve user experience.}
\resumeItem{\textbf{Impact:} Delivered responsive UI and faster load times, boosting user engagement, and ensuring cross-browser compatibility.}
\resumeItem{\textbf{Impact:} Increased conversion rate by 25\% through streamlined checkout flow and optimized UX, demonstrating analytical skills.}
\resumeItem{\textbf{Performance:} Integrated Stripe and optimized queries, reducing transaction time by 35\%, while ensuring security and data protection.}
\resumeItemListEnd



\vspace{-15pt}

\resumeProjectHeading
{\href{https://smart-recruit-green.vercel.app/}{\textbf{\textcolor{customblue}{Smart Recruit - AI-Powered Candidate Evaluation Platform}}} $|$ \emph{Next.js, Gemini API, CSS, MongoDB}}
{}
\resumeItemListStart
\resumeItem{\textbf{Application:} Built an AI tool for HRs to evaluate candidates by comparing resumes with job descriptions, following Agile methodologies.}
\resumeItem{\textbf{Key Features:} Added compatibility scoring, feedback (skills, experience, gaps), and ranking for better hiring decisions, improving software performance and efficiency.}
\resumeItem{\textbf{Responsive Design:} Delivered consistent user experience across devices, ensuring cross-device interfaces were optimized for different screen sizes.}
\resumeItem{\textbf{Impact:} Achieved 90\% accuracy in job-candidate matching using AI-driven resume parsing, demonstrating strong problem-solving skills.}
\resumeItem{\textbf{Impact:} Reduced candidate screening time by 40\%, improving recruiter efficiency and decision-making speed, reflecting business acumen and strategic thinking.}
\resumeItemListEnd



\resumeSubHeadingListEnd
\vspace{-10pt}

%-----------SKILLS-----------
\section{Skills Summary}
\vspace{5pt}
\begin{itemize}[leftmargin=0.15in, label={}]
\item
\small{\textbf{Technical Skills:} JavaScript, TypeScript, HTML5, CSS3, SQL, Git, REST APIs.} \\
\item
\small{\textbf{Frameworks and Libraries:} React.js, Next.js, Node.js, Express.js, REDUX.} \\
\item
\small{\textbf{Databases:} MongoDB (NoSQL with Mongoose), MySQL, PostgreSQL.} \\
\item
\small{\textbf{Tools and Platforms:} Git, GitHub, VSCode, Vercel, Render, Salesforce} \\
\item
\small{\textbf{Development Expertise:} Agile methodologies, Cross-Browser Compatibility, Troubleshooting Issues, Analytical Skills, Database Management, State Management, MERN Stack Development, Responsive Design, Cross-Device Interfaces, WCAG Compliance, API Integration, Data Fetching, Caching, Error Handling, Performance Optimization, Unit Testing, Integration Testing, CI/CD Pipelines, Security and Data Protection.}
\end{itemize}

%-----------EDUCATION及ひび-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Bipin Tripathi Kumaun Institute of Technology Dwarahat, Almora}{Uttarakhand, India}
{Bachelor of Technology; CGPA: 7.1}{August 2020 -- June 2024}
\resumeSubHeadingListEnd

\end{document}